---
title: "Modeling and prediction for movies"
output: 
  html_document: 
    fig_height: 4
    highlight: pygments
    theme: spacelab
---

## Setup

### Load packages

```{r load-packages, message = FALSE}
library(statsr)
library(ggplot2)
library(dplyr)
```

### Load data

Make sure your data and R Markdown files are in the same directory. When loaded
your data file will be called `movies`. Delete this note when before you submit 
your work. 

```{r load-data}
setwd(dir = "C:/Users/Khémon/Documents/R/stats-coursera/linear-regression-modeling/final project")
load("movies.Rdata")
```


* * *

## Part 1: Data

Data: (3 points) Describe how the observations in the sample are collected, and the implications of this data collection method on the scope of inference (generalizability / causality).

According to the codebook, the data set is comprised of 651 randomly sampled movies produced and released before 2016.

Random sampling : the assesment conclusions will be generalizable ! 
If it's a random assesment, conclusions will be both causal and generalizable
We will not be able to conclude causation if our assesment is not random;

* * *

## Part 2: Research question
What are the main variables explaining the success of a given movie. 
By determining what are the main variable associated to a movie success we would be able to predict for a new movie what is its expected success (audiance score).

* * *

## Part 3: Exploratory data analysis

NOTE: Insert code chunks as needed by clicking on the "Insert a new code chunk" 
button above. Make sure that your code is visible in the project you submit. 
Delete this note when before you submit your work.

We first want to explore our data, and see what is the distribution of movies by genre
```{r movies genre histogram }
plot(movies$genre)
#mosaicplot(movies$thtr_rel_year ~ movies$genre)
```
Most of movies (almost 50%) are from the "Drama" genre. 
Then, come "Comedy", "Action & Adventure" and "Mystery & Suspense". 

We continue exploring different caracteristics of movie, looking at runtimes
```{r movies runtime }
hist(movies$runtime)

```
A typical movie last form 90 min to 120

Same for imdb ratings
```{r imdb rating distr}
#scatter plot
plot(movies$imdb_rating)
# distribution
hist(movies$imdb_rating)
# box plot
boxplot(movies$imdb_rating)
# imdb rating summary
summary(movies$imdb_rating)
```
50% are in a range  between 5.9 (1st qt) and 7.3 (3rd qt)

Number of votes imdb 
```{r imdb rating distr}
plot(movies$imdb_num_votes)
hist(movies$imdb_num_votes)
```

Imdb ratings distribution is left skewed 
Evolution of rating througout time (year of theater)
```{r imdb rating plot  evol}
# distribution
ggplot(data=movies, aes(x=thtr_rel_year, y=imdb_rating)) + geom_point()

ggplot(data=movies, aes(x=thtr_rel_year, y=imdb_rating)) + geom_jitter()

ggplot(data=movies, aes(x=thtr_rel_year, y=imdb_rating)) + geom_jitter() + geom_line(method = lm)

```
The line of linear regression seems to demonstrate the slope is almost 0 so that there appears to be no linear correlation between the year and ratings. 


Critics score:
```{r critics score by drama }
plot(movies$critics_score)
boxplot(movies$critics_score)
ggplot(data = movies, aes(x=genre, y = critics_score)) + geom_point()
```


audience score:
```{r audience score}
plot(movies$audience_score)
ggplot(data = movies, aes(x=genre, y = audience_score)) + geom_point()

```


audience rating:
```{r audience rating }
plot(movies$audience_rating)

```




* * *

## Part 4: Modeling
Develop a multiple linear regression model to predict a numerical variable in the dataset. The response variable and the explanatory variables can be existing variables in the dataset, or new variables you create based on existing variables.

response variable: audiance_score

explatory variables: 

title_type: Type of movie (Documentary, Feature Film, TV Movie)
genre: Genre of movie (Action & Adventure, Comedy, Documentary, Drama, Horror, Mystery & Suspense, Other)
runtime: Runtime of movie (in minutes)
mpaa_rating: MPAA rating of the movie (G, PG, PG-13, R, Unrated)
studio: Studio that produced the movie
thtr_rel_year: Year the movie is released in theaters

dvd_rel_year: Year the movie is released on DVD

imdb_rating: Rating on IMDB
imdb_num_votes: Number of votes on IMDB
critics_rating: Categorical variable for critics rating on Rotten Tomatoes (Certified Fresh, Fresh, Rotten)
critics_score: Critics score on Rotten Tomatoes
audience_score: Audience score on Rotten Tomatoes
best_pic_nom: Whether or not the movie was nominated for a best picture Oscar (no, yes)
best_pic_win: Whether or not the movie won a best picture Oscar (no, yes)
best_actor_win: Whether or not one of the main actors in the movie ever won an Oscar (no, yes) - note that this is not necessarily whether the actor won an Oscar for their role in the given movie
best_actress win: Whether or not one of the main actresses in the movie ever won an Oscar (no, yes) - not that this is not necessarily whether the actresses won an Oscar for their role in the given movie
best_dir_win: Whether or not the director of the movie ever won an Oscar (no, yes) - not that this is not necessarily whether the director won an Oscar for the given movie
top200_box: Whether or not the movie is in the Top 200 Box Office list on BoxOfficeMojo (no, yes)


We removed following variables from the model:
audience_rating: Categorical variable for audience rating on Rotten Tomatoes (Spilled, Upright)
director: Director of the movie
actor1-actor5: List of first 5 main actors in the movie (abridged cast), this information was used to determine whether the movie casts an actor or actress who won a best actor or actress Oscar
rt_url: Link to Rotten Tomatoes page for the movie
imdb_url: Link to IMDB page for the movie
imdb_id: IMDB ID of the movie
thtr_rel_month: Month the movie is released in theaters
thtr_rel_day: Day of the month the movie is released in theaters
dvd_rel_month: Month the movie is released on DVD
dvd_rel_day: Day of the month the movie is released on DVD

```{r full linear model}

mfull = lm(data = movies, audience_score~ title_type+genre+runtime+mpaa_rating+studio+thtr_rel_year+thtr_rel_month+thtr_rel_day+dvd_rel_year+dvd_rel_month+dvd_rel_day+imdb_rating+imdb_num_votes+critics_rating+critics_score+audience_rating+best_pic_nom+best_pic_win+best_actor_win+best_actress_win+best_dir_win+top200_box)

summary(mfull)
```

Excluding variables: 

```{r colinearity test with imdb rating}
ggplot(data = movies, aes(x=imdb_rating, y = audience_score)) + geom_point() + geom_smooth(method= lm)
cor(movies$imdb_rating, movies$audiance_score)
test = lm(audience_score ~ imdb_rating, data = movies)
summary(test)
```
imdb_rating has really strong correlation with the 

same goes for audience_rating.

Analysis of collinearity on critics score
```{r colinearity test with imdb rating}
ggplot(data = movies, aes(x=critics_score, y = audience_score)) + geom_point() + geom_smooth(method= lm)
cor(movies$critics_score, movies$audience_score)
test = lm(audience_score ~ critics_score, data = movies)
summary(test)
```
Critics score is also strongly correlated with audience_score


We remove those 3 variables from the model.
studio: we chose to remove this variable also. The slope of each studio
The slope is really low. So we can say that it's not significant, and we rather have a more simple model. 
We can remove also the number of votes (imdb) as it don't seem to bring any more information to the table 
```{r linear model}

mfull = lm(data = movies, audience_score~ title_type+genre+runtime+mpaa_rating
           +thtr_rel_year+dvd_rel_year+best_pic_nom+best_pic_win+best_actor_win+best_actress_win+best_dir_win+top200_box)

summary(mfull)
```

Let's create another data frame which is a subset of movies data frame, that contains only variables that will be used in our analysis. 

```{r}
 movies_small = movies[, c("audience_score", "title_type","genre","runtime",                           "mpaa_rating","studio","thtr_rel_year","dvd_rel_year","imdb_rating","imdb_num_votes","critics_rating","critics_score","audience_rating","best_pic_nom","best_pic_win","best_actor_win","best_actress_win","best_dir_win","top200_box")]
```



```{r}

#Full model
full_model = lm (audience_score ~ title_type+genre+runtime+mpaa_rating+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+critics_rating+critics_score+audience_rating+best_pic_nom+best_pic_win+best_actor_win+best_actress_win+best_dir_win+top200_box, data=movies_small)
#summary full model R squared = 0.885
summary(full_model)

r.squared = c()

# m1 remove title_type
m1 = lm(audience_score ~ genre+runtime+mpaa_rating+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+critics_rating+critics_score+audience_rating+best_pic_nom+best_pic_win+best_actor_win+best_actress_win+best_dir_win+top200_box, data=movies_small)
r.squared['title_type'] = summary(m1)$adj.r.squared


# m2 remove genre
m2 = lm(audience_score ~ title_type+runtime+mpaa_rating+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+critics_rating+critics_score+audience_rating+best_pic_nom+best_pic_win+best_actor_win+best_actress_win+best_dir_win+top200_box, data=movies_small)
r.squared['genre'] = summary(m2)$adj.r.squared

# remove runtime
m3 = lm(audience_score ~ title_type+genre+mpaa_rating+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+critics_rating+critics_score+audience_rating+best_pic_nom+best_pic_win+best_actor_win+best_actress_win+best_dir_win+top200_box, data=movies_small)
r.squared['runtime'] = summary(m3)$adj.r.squared


# remove imdb rating
m4 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_num_votes+critics_rating+critics_score+audience_rating+best_pic_nom+best_pic_win+best_actor_win+best_actress_win+best_dir_win+top200_box, data=movies_small)
r.squared['imdb_rating'] = summary(m4)$adj.r.squared

# remove imdb num votes
m5 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+critics_rating+critics_score+audience_rating+best_pic_nom+best_pic_win+best_actor_win+best_actress_win+best_dir_win+top200_box, data=movies_small)
r.squared['imdb_num_votes'] <- summary(m5)$adj.r.squared

# remove audience_rating
m6 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+critics_rating+critics_score+best_pic_nom+best_pic_win+best_actor_win+best_actress_win+best_dir_win+top200_box, data=movies_small)
r.squared['audience_rating'] = summary(m6)$adj.r.squared

# remove audience_rating
m7 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+audience_rating+critics_rating+best_pic_nom+best_pic_win+best_actor_win+best_actress_win+best_dir_win+top200_box, data=movies_small)
r.squared['audience_rating'] = summary(m7)$adj.r.squared


# remove critics_rating
m8 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+audience_rating+best_pic_nom+best_pic_win+best_actor_win+best_actress_win+best_dir_win+top200_box, data=movies_small)
r.squared['critics_rating'] = summary(m8)$adj.r.squared


# remove best_actor_win
m9 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+audience_rating+critics_rating+best_pic_nom+best_pic_win+best_actress_win+best_dir_win+top200_box, data=movies_small)
r.squared['best_actor_win'] = summary(m9)$adj.r.squared

# remove best_pic_nom
m10 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+audience_rating+critics_rating+best_actor_win+best_pic_win+best_actress_win+best_dir_win+top200_box, data=movies_small)
r.squared['best_pic_nom'] = summary(m10)$adj.r.squared

which(r.squared == max(r.squared))

```
We remove the critics rating 

```{r}

#we update model target with model without critics rating
model_cible = m8
#summary full model R squared = 0.8855
summary(model_cible)

r.squared = c()

# m1 remove title_type
m1 = lm(audience_score ~ genre+runtime+mpaa_rating+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+critics_score+audience_rating+best_pic_nom+best_pic_win+best_actor_win+best_actress_win+best_dir_win+top200_box, data=movies_small)
r.squared['title_type'] = summary(m1)$adj.r.squared


# m2 remove genre
m2 = lm(audience_score ~ title_type+runtime+mpaa_rating+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+critics_score+audience_rating+best_pic_nom+best_pic_win+best_actor_win+best_actress_win+best_dir_win+top200_box, data=movies_small)
r.squared['genre'] = summary(m2)$adj.r.squared

# remove runtime
m3 = lm(audience_score ~ title_type+genre+mpaa_rating+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+critics_score+audience_rating+best_pic_nom+best_pic_win+best_actor_win+best_actress_win+best_dir_win+top200_box, data=movies_small)
r.squared['runtime'] = summary(m3)$adj.r.squared


# remove imdb rating
m4 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_num_votes+critics_score+audience_rating+best_pic_nom+best_pic_win+best_actor_win+best_actress_win+best_dir_win+top200_box, data=movies_small)
r.squared['imdb_rating'] = summary(m4)$adj.r.squared

# remove imdb num votes
m5 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+critics_score+audience_rating+best_pic_nom+best_pic_win+best_actor_win+best_actress_win+best_dir_win+top200_box, data=movies_small)
r.squared['imdb_num_votes'] <- summary(m5)$adj.r.squared

# remove audience_rating
m6 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+critics_score+best_pic_nom+best_pic_win+best_actor_win+best_actress_win+best_dir_win+top200_box, data=movies_small)
r.squared['audience_rating'] = summary(m6)$adj.r.squared

# remove audience_rating
m7 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+audience_rating+best_pic_nom+best_pic_win+best_actor_win+best_actress_win+best_dir_win+top200_box, data=movies_small)
r.squared['audience_rating'] = summary(m7)$adj.r.squared



# remove best_actor_win
m9 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+audience_rating+best_pic_nom+best_pic_win+best_actress_win+best_dir_win+top200_box, data=movies_small)
r.squared['best_actor_win'] = summary(m9)$adj.r.squared

# remove best_pic_nom
m10 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+audience_rating+best_actor_win+best_pic_win+best_actress_win+best_dir_win+top200_box, data=movies_small)
r.squared['best_pic_nom'] = summary(m10)$adj.r.squared

# remove best_actress_win
m11 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+audience_rating+best_actor_win+best_pic_nom+best_pic_win+best_dir_win+top200_box, data=movies_small)
r.squared['best_actress_win'] = summary(m11)$adj.r.squared

# remove best_dir_win
m12 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+audience_rating+best_actor_win+best_pic_nom+best_pic_win+best_actress_win+top200_box, data=movies_small)
r.squared['best_dir_win'] = summary(m12)$adj.r.squared

# remove top200_box
m13 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+audience_rating+best_actor_win+best_pic_nom+best_pic_win+best_actress_win+best_dir_win, data=movies_small)
r.squared['best_dir_win'] = summary(m13)$adj.r.squared

which(r.squared == max(r.squared))

```
We remove best dir win

```{r}
#we update model target with model without best director win
model_cible = m12
#summary full model R squared = 0.8855
summary(model_cible)


r.squared = c()

# m1 remove title_type
m1 = lm(audience_score ~ genre+runtime+mpaa_rating+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+critics_score+audience_rating+best_pic_nom+best_pic_win+best_actor_win+best_actress_win+top200_box, data=movies_small)
r.squared['title_type'] = summary(m1)$adj.r.squared


# m2 remove genre
m2 = lm(audience_score ~ title_type+runtime+mpaa_rating+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+critics_score+audience_rating+best_pic_nom+best_pic_win+best_actor_win+best_actress_win+top200_box, data=movies_small)
r.squared['genre'] = summary(m2)$adj.r.squared

# remove runtime
m3 = lm(audience_score ~ title_type+genre+mpaa_rating+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+critics_score+audience_rating+best_pic_nom+best_pic_win+best_actor_win+best_actress_win+top200_box, data=movies_small)
r.squared['runtime'] = summary(m3)$adj.r.squared


# remove imdb rating
m4 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_num_votes+critics_score+audience_rating+best_pic_nom+best_pic_win+best_actor_win+best_actress_win+top200_box, data=movies_small)
r.squared['imdb_rating'] = summary(m4)$adj.r.squared

# remove imdb num votes
m5 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+critics_score+audience_rating+best_pic_nom+best_pic_win+best_actor_win+best_actress_win+top200_box, data=movies_small)
r.squared['imdb_num_votes'] <- summary(m5)$adj.r.squared

# remove audience_rating
m6 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+critics_score+best_pic_nom+best_pic_win+best_actor_win+best_actress_win+top200_box, data=movies_small)
r.squared['audience_rating'] = summary(m6)$adj.r.squared

# remove audience_rating
m7 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+audience_rating+best_pic_nom+best_pic_win+best_actor_win+best_actress_win+top200_box, data=movies_small)
r.squared['audience_rating'] = summary(m7)$adj.r.squared



# remove best_actor_win
m9 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+audience_rating+best_pic_nom+best_pic_win+best_actress_win+top200_box, data=movies_small)
r.squared['best_actor_win'] = summary(m9)$adj.r.squared

# remove best_pic_nom
m10 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+audience_rating+best_actor_win+best_pic_win+best_actress_win+top200_box, data=movies_small)
r.squared['best_pic_nom'] = summary(m10)$adj.r.squared

# remove best_actress_win
m11 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+audience_rating+best_actor_win+best_pic_nom+best_pic_win+top200_box, data=movies_small)
r.squared['best_actress_win'] = summary(m11)$adj.r.squared


# remove top200_box
m13 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+audience_rating+best_actor_win+best_pic_nom+best_pic_win+best_actress_win+best_dir_win, data=movies_small)
r.squared['best_dir_win'] = summary(m13)$adj.r.squared

which(r.squared == max(r.squared))

```
We remove best actor win


```{r}
#we update model target with model without best actor
model_cible = m11
#summary full model R squared = 0.8855
summary(model_cible)


r.squared = c()

# m1 remove title_type
m1 = lm(audience_score ~ genre+runtime+mpaa_rating+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+critics_score+audience_rating+best_pic_nom+best_pic_win+best_actress_win+top200_box, data=movies_small)
r.squared['title_type'] = summary(m1)$adj.r.squared


# m2 remove genre
m2 = lm(audience_score ~ title_type+runtime+mpaa_rating+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+critics_score+audience_rating+best_pic_nom+best_pic_win+best_actress_win+top200_box, data=movies_small)
r.squared['genre'] = summary(m2)$adj.r.squared

# remove runtime
m3 = lm(audience_score ~ title_type+genre+mpaa_rating+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+critics_score+audience_rating+best_pic_nom+best_pic_win+best_actress_win+top200_box, data=movies_small)
r.squared['runtime'] = summary(m3)$adj.r.squared


# remove imdb rating
m4 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_num_votes+critics_score+audience_rating+best_pic_nom+best_pic_win+best_actress_win+top200_box, data=movies_small)
r.squared['imdb_rating'] = summary(m4)$adj.r.squared

# remove imdb num votes
m5 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+critics_score+audience_rating+best_pic_nom+best_pic_win+best_actress_win+top200_box, data=movies_small)
r.squared['imdb_num_votes'] <- summary(m5)$adj.r.squared

# remove audience_rating
m6 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+critics_score+best_pic_nom+best_pic_win+best_actress_win+top200_box, data=movies_small)
r.squared['audience_rating'] = summary(m6)$adj.r.squared

# remove critics_score
m7 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+audience_rating+best_pic_nom+best_pic_win+best_actress_win+top200_box, data=movies_small)
r.squared['critics_score'] = summary(m7)$adj.r.squared



# remove best_pic_nom
m9 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+critics_score+audience_rating+best_pic_win+best_actress_win+top200_box, data=movies_small)
r.squared['best_pic_nom'] = summary(m9)$adj.r.squared

# remove best_pic_win
m10 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+audience_rating+best_pic_nom+best_actress_win+top200_box, data=movies_small)
r.squared['best_pic_win'] = summary(m10)$adj.r.squared

# remove best_actress_win
m11 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+audience_rating+best_pic_nom+best_pic_win+top200_box, data=movies_small)
r.squared['best_actress_win'] = summary(m11)$adj.r.squared


# remove top200_box
m13 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+audience_rating+best_pic_nom+best_pic_win+best_actress_win+best_dir_win, data=movies_small)
r.squared['top200_box'] = summary(m13)$adj.r.squared

which(r.squared == max(r.squared))
```
We remove best_pic_win

```{r}
#we update model target with model without best pic win
model_cible = m10
#summary full model R squared = 0.8855
summary(model_cible)


r.squared = c()

# m1 remove title_type
m1 = lm(audience_score ~ genre+runtime+mpaa_rating+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+critics_score+audience_rating+best_pic_nom+best_actress_win+top200_box, data=movies_small)
r.squared['title_type'] = summary(m1)$adj.r.squared


# m2 remove genre
m2 = lm(audience_score ~ title_type+runtime+mpaa_rating+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+critics_score+audience_rating+best_pic_nom+best_actress_win+top200_box, data=movies_small)
r.squared['genre'] = summary(m2)$adj.r.squared

# remove runtime
m3 = lm(audience_score ~ title_type+genre+mpaa_rating+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+critics_score+audience_rating+best_pic_nom+best_actress_win+top200_box, data=movies_small)
r.squared['runtime'] = summary(m3)$adj.r.squared


# remove imdb rating
m4 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_num_votes+critics_score+audience_rating+best_pic_nom+best_actress_win+top200_box, data=movies_small)
r.squared['imdb_rating'] = summary(m4)$adj.r.squared

# remove imdb num votes
m5 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+critics_score+audience_rating+best_pic_nom+best_actress_win+top200_box, data=movies_small)
r.squared['imdb_num_votes'] <- summary(m5)$adj.r.squared

# remove audience_rating
m6 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+critics_score+best_pic_nom+best_actress_win+top200_box, data=movies_small)
r.squared['audience_rating'] = summary(m6)$adj.r.squared

# remove critics_score
m7 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+audience_rating+best_pic_nom+best_actress_win+top200_box, data=movies_small)
r.squared['critics_score'] = summary(m7)$adj.r.squared


# remove best_pic_nom
m9 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+critics_score+audience_rating+best_actress_win+top200_box, data=movies_small)
r.squared['best_pic_nom'] = summary(m9)$adj.r.squared


# remove best_actress_win
m11 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+audience_rating+best_pic_nom+top200_box, data=movies_small)
r.squared['best_actress_win'] = summary(m11)$adj.r.squared


# remove top200_box
m13 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+audience_rating+best_pic_nom+best_actress_win+best_dir_win, data=movies_small)
r.squared['top200_box'] = summary(m13)$adj.r.squared

which(r.squared == max(r.squared))
r.squared

```

We remove top200_box

```{r}
#we update model target with model without top200_box
model_cible = m13
#summary full model R squared = 0.886
summary(model_cible)


r.squared = c()

# m1 remove title_type
m1 = lm(audience_score ~ genre+runtime+mpaa_rating+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+critics_score+audience_rating+best_pic_nom+best_actress_win, data=movies_small)
r.squared['title_type'] = summary(m1)$adj.r.squared


# m2 remove genre
m2 = lm(audience_score ~ title_type+runtime+mpaa_rating+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+critics_score+audience_rating+best_pic_nom+best_actress_win, data=movies_small)
r.squared['genre'] = summary(m2)$adj.r.squared

# remove runtime
m3 = lm(audience_score ~ title_type+genre+mpaa_rating+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+critics_score+audience_rating+best_pic_nom+best_actress_win, data=movies_small)
r.squared['runtime'] = summary(m3)$adj.r.squared


# remove imdb rating
m4 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_num_votes+critics_score+audience_rating+best_pic_nom+best_actress_win, data=movies_small)
r.squared['imdb_rating'] = summary(m4)$adj.r.squared

# remove imdb num votes
m5 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+critics_score+audience_rating+best_pic_nom+best_actress_win, data=movies_small)
r.squared['imdb_num_votes'] <- summary(m5)$adj.r.squared

# remove audience_rating
m6 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+critics_score+best_pic_nom+best_actress_win, data=movies_small)
r.squared['audience_rating'] = summary(m6)$adj.r.squared

# remove critics_score
m7 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+audience_rating+best_pic_nom+best_actress_win, data=movies_small)
r.squared['critics_score'] = summary(m7)$adj.r.squared


# remove best_pic_nom
m9 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+critics_score+audience_rating+best_actress_win, data=movies_small)
r.squared['best_pic_nom'] = summary(m9)$adj.r.squared


# remove best_actress_win
m11 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+imdb_num_votes+audience_rating+best_pic_nom, data=movies_small)
r.squared['best_actress_win'] = summary(m11)$adj.r.squared



which(r.squared == max(r.squared))
r.squared

```
We remove imdb_num_votes 

```{r}
#we update model target with model without imdb votes
model_cible = m5
#summary full model R squared = 0.886
summary(model_cible)


r.squared = c()

# m1 remove title_type
m1 = lm(audience_score ~ genre+runtime+mpaa_rating+studio+thtr_rel_year+dvd_rel_year+imdb_rating+critics_score+audience_rating+best_pic_nom+best_actress_win, data=movies_small)
r.squared['title_type'] = summary(m1)$adj.r.squared


# m2 remove genre
m2 = lm(audience_score ~ title_type+runtime+mpaa_rating+studio+thtr_rel_year+dvd_rel_year+imdb_rating+critics_score+audience_rating+best_pic_nom+best_actress_win, data=movies_small)
r.squared['genre'] = summary(m2)$adj.r.squared

# remove runtime
m3 = lm(audience_score ~ title_type+genre+mpaa_rating+studio+thtr_rel_year+dvd_rel_year+imdb_rating+critics_score+audience_rating+best_pic_nom+best_actress_win, data=movies_small)
r.squared['runtime'] = summary(m3)$adj.r.squared


# remove imdb rating
m4 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+critics_score+audience_rating+best_pic_nom+best_actress_win, data=movies_small)
r.squared['imdb_rating'] = summary(m4)$adj.r.squared

# remove audience_rating
m6 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+critics_score+best_pic_nom+best_actress_win, data=movies_small)
r.squared['audience_rating'] = summary(m6)$adj.r.squared

# remove critics_score
m7 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+audience_rating+best_pic_nom+best_actress_win, data=movies_small)
r.squared['critics_score'] = summary(m7)$adj.r.squared


# remove best_pic_nom
m9 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+critics_score+audience_rating+best_actress_win, data=movies_small)
r.squared['best_pic_nom'] = summary(m9)$adj.r.squared


# remove best_actress_win
m11 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+audience_rating+best_pic_nom, data=movies_small)
r.squared['best_actress_win'] = summary(m11)$adj.r.squared



which(r.squared == max(r.squared))
r.squared
```

We remove critics_score

```{r}

#we update model target with model without critics score
model_cible = m7
#summary full model R squared = 0.8864514
summary(model_cible)

r.squared = c()

# m1 remove title_type
m1 = lm(audience_score ~ genre+runtime+mpaa_rating+studio+thtr_rel_year+dvd_rel_year+imdb_rating+audience_rating+best_pic_nom+best_actress_win, data=movies_small)
r.squared['title_type'] = summary(m1)$adj.r.squared


# m2 remove genre
m2 = lm(audience_score ~ title_type+runtime+mpaa_rating+studio+thtr_rel_year+dvd_rel_year+imdb_rating+audience_rating+best_pic_nom+best_actress_win, data=movies_small)
r.squared['genre'] = summary(m2)$adj.r.squared

# remove runtime
m3 = lm(audience_score ~ title_type+genre+mpaa_rating+studio+thtr_rel_year+dvd_rel_year+imdb_rating+audience_rating+best_pic_nom+best_actress_win, data=movies_small)
r.squared['runtime'] = summary(m3)$adj.r.squared


# remove imdb rating
m4 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+audience_rating+best_pic_nom+best_actress_win, data=movies_small)
r.squared['imdb_rating'] = summary(m4)$adj.r.squared

# remove audience_rating
m6 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+best_pic_nom+best_actress_win, data=movies_small)
r.squared['audience_rating'] = summary(m6)$adj.r.squared


# remove best_pic_nom
m9 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+audience_rating+best_actress_win, data=movies_small)
r.squared['best_pic_nom'] = summary(m9)$adj.r.squared


# remove best_actress_win
m11 = lm(audience_score ~ title_type+genre+runtime+studio+thtr_rel_year+dvd_rel_year+imdb_rating+audience_rating+best_pic_nom, data=movies_small)
r.squared['best_actress_win'] = summary(m11)$adj.r.squared



which(r.squared == max(r.squared))
r.squared
```


We cannot go further, without reducing adjusted R^2. 

Remaining variable: 
title_type
genre
runtime
studio
theater release year
dvd release year
imdb rating
audience rating
best picture nominated
best actress wins
```{r}

#final model
summary(model_cible)

```

Audience rating is obviously the variable the  most correlated with audiance score. Because it depends actually on the score. 


* * *


## Part 5: Prediction

NOTE: Insert code chunks as needed by clicking on the "Insert a new code chunk" 
button above. Make sure that your code is visible in the project you submit. 
Delete this note when before you submit your work.

* * *

## Part 6: Conclusion

